---
title: "Exam admin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{admin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
pacman::p_load(tidyverse, examMarkR)
```

To help with the admin of exam marking, there are a few helper functions. 

# Grade roster

The function `fill_grade_roster()` will put the marks into the blank grade roster. 

For this example, we have a grade roster

```{r}
grade_roster  <- read_lines("../inst/grade_example.csv")
grade_roster
```

Also we need the totals to be rounded. As an example, I have included an example set of data


```{r}
SMI_2018_marks_clean
```

For grade rosters, the total must be rounded to the nearest integer:

```{r}
SMI_2018_marks_clean  <- 
  SMI_2018_marks_clean %>% 
  mutate(
    Total = round(Total)
  )
```

To fill the grade roster, you give the column 

```{r}
SMI_2018_marks_clean %>% 
  exam_fill_grade_roster(ID, Total,
                  infile = "../inst/grade_example.csv",
                  outfile = "../inst/example_output.csv")
```

```{r}
grade_roster  <- read_lines("../inst/example_output.csv")
grade_roster
```

**IMPORTANT**

**This is the grade roster - open it and check that it is correct.**

This function will automatically add `FNS` if mark is 0 and also `US10` for marks between 45 and 49, this can be changed for first year courses. 

Also you can pass in a vector of IDs that have a RP mark, e.g., pending a plagiarism decision. 

# Emailing

To help with email, there is a short helper function that will take a vector of IDs and return them as a string that you can paste into an email. 

```{r}
IDs  <- c('a1078881', 'a1078886')
exam_get_email_list(IDs)
```


# Get enrolled students

As the canvas grade book can be out of date with regard to enrolment, then I advise using the grade roster as the most up-to-date information. The function `exam_get_enrolled()` takes the grade roster and returns the students info. 
`
```{r}
exam_get_enrolled("../inst/grade_example.csv")
```


# Auditing

For auditing, we need to choose 10% of the results to check. The function `exam_run_audit()` will give those results close to the boundaries of 50, 65, 75, and 85. If more are needed, then you change change the width and the boundaries. 

```{r}
exam_run_audit(SMI_2018_marks_clean, Total)
```

