---
title: "Case study"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case_study}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(examMarkR)
library(tidyverse)
```

# Getting data

In this case, we have some built in raw data that we will use:

```{r}
raw_data
```

The form of the data is a row for each  student with 

- Student ID, 
- Assignment1 to  Assignment 5, 
- Project,
- Online quizzes Model selection to ANCOVA, and 
- Exam questions Q1 to Q6. 

# Cleaning the data

## Rename columns

First we rename the columns

```{r}
colnames(raw_data)  <- c("ID", 
                         str_c("A", 1:5), 
                         "P", 
                         str_c("OQ0", 1:8), 
                         str_c("Q", 1:6))
raw_data
```

## Exemptions

In canvas any piece of assessment that has not be submitted has a blank cell. When we import this into R, it is represented by an NA. Also any exemptions in canvas are indicated as EX. 

We would like to set missing marks to 0, and then exemptions to missing. This way any exemption will not be incorporated into the final mark. 

The function to do this is 

```{r}
marks  <- 
  raw_data %>% 
  exam_canvas_clean("^A|^P|^OQ|^Q")
marks
```

This function takes a data frame and  a regular expression. In this case we choose all  columns that start with an  A, or a P, or OQ, or Q. 

# Consolidate marks

## Get totals

For the exam, we have the marks for each question, but not the total exam mark. We will add this. 

```{r}
marks  <- 
  marks %>% 
  mutate(
    E = exam_calculate_total(marks, "^Q")
  )
marks
```


## Convert to proportions

First, we will convert all of the marks to proportions. This is done with `exam_calculate_prop()`. Again this takes a data frame and a regular expression. It also assumes that one of the rows has the totals. 

```{r}
marks  <- 
  marks %>% 
  exam_calculate_prop("^A|^P|^OQ|^Q|E", 1)
marks
```

## Get mean proportion

For the assignments and online quizzes, we will now get the mean proportion. 

```{r}
marks  <- 
  marks %>% 
  mutate(
    A = exam_calculate_mean(marks, "^A"), 
    OQ = exam_calculate_mean(marks, "^OQ"))
marks
```

## Convert to percentage of course

So in this course, we have the following percentages

- exam 70%
- assignment 20%
- online quizzes 5%, and 
- project 5%. 

```{r}
marks  <- 
  marks %>% 
  mutate(
    E_70 = E * 70, 
    A_20 = A * 20, 
    OQ_5 = OQ * 5, 
    P_5 = P * 5
  )
marks
```

## Get total for course

Get total and also round. 

```{r}
marks  <- 
  marks %>% 
  mutate(
    total = E_70 + A_20 + OQ_5 + P_5, 
    total = round(total))
marks
```


## Grading

The grading scale is 

```{r, echo=FALSE}
grade_tab <- tibble(
  grade = c("FNS","FNA","FA","P","C","D","HD"),
  lower = c(0, 1,  45, 50, 65, 75, 85),
  upper = c(0, 44, 49, 64, 74, 84, 100)
)
grade_tab %>% knitr::kable()
```

We get this with the function `exam_grade()`. You can pass your own grade table. As well, if you set `first_year = TRUE`, it set Academic RAA to 40-49 rather than the usual 45-49. 

```{r}
marks  <- 
  marks %>% 
  mutate(
    grade = exam_grade(total)
  )
marks
```

```{r, include = FALSE}
usethis::use_data(marks, overwrite = TRUE)
```

