---
title: "Exam plotting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exam_plotting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  out.width = '100%', 
  fig.width = 10, 
  fig.height = 10
)
```

```{r setup}
pacman::p_load(tidyverse, examMarkR)
```

# Load some data

```{r}
SMI_2018_marks_clean
```

# Plots

## `exam_plot_assessment()`

This is the first one. It will give an over view of the assessment parts of a course for each student. 

```{r}
SMI_2018_marks_clean %>% 
  exam_plot_assessment("^E$|^A$|^OQ$", name = ID, grade = grade)
```

## `exam_plot_grades()`

This one gives the proportion for each grade. 

```{r}
SMI_2018_marks_clean %>% exam_plot_grades(grade)
```

## `exam_plot_profile()`

This idea of this plot is to examine if the exam works. By this, we want to see two things:

1. Is there a good seperation between the grades in each question of the exam?
2. Is the average mark - black dots - what you expected from your setting of the question?

```{r}
SMI_2018_marks_clean %>% exam_plot_profile("^Q", grade)
```

## `exam_plot_norm()`

The final one is to compare the result from the raw marks and the scaled marks. 


```{r}
SMI_2018_marks_clean %>% 
  mutate(
  norm_mark  = exam_norm_linear(Total, tibble(x = 45, y = 50))
  ) %>% 
  exam_plot_norm(Total, norm_mark)
```

