---
title: "Scaling data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{normalization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  out.width = '100%', 
  fig.align = 'center', 
  fig.width = 10, 
  fig.height = 10
)
```

```{r setup}
pacman::p_load(tidyverse, examMarkR)
```

# Type of normalisation

In the package, we have three scaling methods so far:

- the Glonek function, 
- linear scaling - also gives tenting, and 
- McCann spike. 

## Glonek function

The Glonek function scales on a logit score

Let $x_i$ be the raw mark of the $i$th student, then the steps are

1. 
$$
y_i = \log\left(\frac{x_i}{100 - x_i}\right)
$$
2. 
$$
y_i^{scale} = a + b\times y_i
$$
3. 
$$
x_i^{scale} = \frac{100e^{y_i^{scale}}}{1 + e^{y_i^{scale}}}
$$

So the two parameters are $a$ and $b$. Examples are given below. 

```{r}
df  <- tibble(
  raw = 0:100, 
  `a = 0.5, b = 1.1` = exam_norm_glonek(raw, 0.5, 1.1),
  `a = 0.5, b = 1.5` = exam_norm_glonek(raw, 0.5, 1.5),
  `a = 0.5, b = 0.9` = exam_norm_glonek(raw, 0.5, 0.9)
)
df %>% 
  pivot_longer(-raw) %>% 
  ggplot(aes(raw, value, col = name)) + 
  geom_point() + 
  geom_segment(aes(x = 0, xend = 100, y = 0, yend = 100), col = 'black') + 
  labs(col = "Parameters")
```

## Linear scaling

In linear scaling, you give a set of boundary points of the form

$$
(x_j, y_j)
$$
where $x_i$ is a raw mark and $y_i$ is the scale mark it is mapped to. We assume that the set of boundary points always have 

$$
(0,0)\text{ and }(100, 100)
$$

_this are added automatically by the function_ 

The mapping is for the $i$th raw mark, $x_i$ is then


$$
y_i = y_j + \frac{y_{j+1} - y_j}{x_{j+1} - x_j}\times(x_i - x_j), \text{ for }x_j \le x_i\le x_{j+1},  
$$

where $y_i$ is the scaled mark for the $i$ student. 

As an example, consider a scaling where

- 45 is mapped to 50, and 
- 75 is mapped to 90. 

The following code shows how to do this and the resultant marks. 

```{r}
boundary_pts  <- tribble(
  ~x, ~y, 
  45, 50, 
  75, 80
)
df  <- tibble(
  x = 0:100
) %>% 
  mutate(
    y = exam_norm_linear(x, boundary_pts = boundary_pts)
  )
df %>% ggplot(aes(x, y)) + geom_point() + 
  geom_point(data = boundary_pts, col = 'red') + 
  geom_segment(aes(x = 0, xend = 100, y = 0, yend = 100))
```

In the case of tenting, there would be a single boundary point passed through. 

## McCann spike

In this case, we just add one to any mark of 49, 64, 74, or 84.

```{r}
df  <- tibble(
  x = 0:100
) %>% 
  mutate(
    y = exam_norm_mccann(x)
  )
df %>% ggplot(aes(x, y)) + geom_point() + 
  geom_segment(aes(x = 0, xend = 100, y = 0, yend = 100))
```

# Comparing scaled and raw marks

To aid in compring the effect of scaling, there are two functions

## `exam_compare_norm()`

This function takes the column of raw and the column of scaled and gives the grade proportions for each. 

Here is scale using the Glonek with $a = 1$ and $b = 1.1$. 

```{r}
marks %>% 
 mutate(norm = exam_norm_glonek(total, a = 1, b = 1.1)) %>% 
   exam_compare_norm(total, norm) %>% 
  knitr::kable()
```


## `exam_plot_norm()`

This one give a comparison plot:

```{r}
marks %>% 
 mutate(norm = exam_norm_glonek(total, a = 1, b = 1.1)) %>% 
   exam_plot_norm(raw = total, norm)
```



